### 2018-01-18 Documents/bootcamp_topic_intro.tex
First Class Outline Fixed

\needspace{2\baselineskip}
\item Course materials
\begin{itemize}
\item Required:  practice, exam, project
\item Google ``nyu data bootcamp''
\item Website, topic list \& links  (thanks, Spencer):\\ \url{https://nyu.data-bootcamp.com/undergrad_outline/}  (bookmark me!)
\item Book: \\ \url{https://www.gitbook.com/book/nyudatabootcamp/data-bootcamp/details}
\item Discussion group: \\ \url{https://groups.google.com/d/forum/databootcamp_fall2017_undergrad}
\item Data page: \\
\url{https://nyu.data-bootcamp.com/data/}
\item GitHub repository:  \url{https://github.com/NYUDataBootcamp/Materials}
\end{itemize}

@@

\section*{\href{https://github.com}{GitHub}}
\begin{itemize}
\item What I will use it for\ldots
\begin{itemize}
\item Source of ALL course materials
\item Place for you to grab materials on the fly. Save files by cut and paste, clever save as, or "Raw" (ask about this)
\end{itemize}
\item You need to create an account and email me your username
\item What you will use it for\ldots
\begin{itemize}
\item Think of this like an artists portfolio. Here you can post your code and projects and show potential employers, family, friends what you have done.
\end{itemize}
\item Now lets use it
\begin{itemize}
\item Put red sticker on your laptop
\item Sign into github (if you do not have an account, create one)
\item Create a new repository and name it \verb|my_first_repository|,
\item place the \verb|my_first_file.csv| file you created in it,
\item Great job! Replace red sticker with green!\\
Next class, I'm going to try and ``pull'' the file and then report some statistics about the class to you.
\end{itemize}
\end{itemize}

@@

\begin{center}
\begin{tabular}{cc}
\toprule
Environment & File or Object \\
\midrule
MS Word  & Word document  \\
 & Excel file     \\
iTunes & \\
%Typewriter & \\
Atom & \\
Spyder   &                \\
\bottomrule
\end{tabular}
\end{center}

\item Run the \verb|Maddison_data_input.py| Python code example.
\begin{itemize}
\item Go to the \verb|Data_Bootcamp| GitHub repository (link above).
\item Navigate to the {\tt Code} directory and {\tt Lab} subdirectory.
\item Get \verb|Maddison_data_input.py|
\begin{itemize}
\item Cut and paste into blank file
\item Or:  Save file in \verb|Data_Bootcamp| directory (ask how)
\end{itemize}
\item Open file in Spyder (File, Open).
\item Run it by clicking on large green triangle.
\item What do you see?
\end{itemize}

\item {\it Only if you have time.\/} Try this program: \verb|OECD_health_indicators.py|.
What do you see?  What questions does it raise?
(There are other files in the same directory, but some of them don't work yet.)

>>>>

\needspace{2\baselineskip}
\item Course materials
\begin{itemize}
\item Required:  practice, exam, project
\item Google ``nyu data bootcamp''
\item Website, topic list \& links  (thanks, Spencer):\\ \url{https://nyu.data-bootcamp.com/undergrad_outline/}  (bookmark me!)
\item Book: \\ \url{https://www.gitbook.com/book/nyudatabootcamp/data-bootcamp/details}
\item Data page: \\
\url{https://nyu.data-bootcamp.com/data/}
\item NYU Data Bootcamp GitHub repository:  \url{https://github.com/NYUDataBootcamp/Materials}
\item My Class Specific GitHub repository: \url{https://github.com/mwaugh0328/data_bootcamp_spring_2018}
\end{itemize}

@@

\section*{\href{https://github.com}{GitHub}}
\begin{itemize}
\item What I will use it for\ldots
\begin{itemize}
\item Source of ALL course materials
\item Place for you to grab materials on the fly. Save files by cut and paste, clever save as, or "Raw" (ask about this)
\end{itemize}
\item You need to create an account and email me your username
\item What you will use it for\ldots
\begin{itemize}
\item Think of this like an artists portfolio. Here you can post your code and projects and show potential employers, family, friends what you have done.
\end{itemize}
\item Now lets use it
\begin{itemize}
\item Put red sticker on your laptop
\item Sign into github (if you do not have an account, create one)
\item Create a new repository and name it \verb|my_first_repository|,
\item place the \verb|bootcamp_test.ipnyb| file you created in it,
\item Great job! Replace red sticker with green!\\
\end{itemize}
\end{itemize}

@@

\begin{center}
\begin{tabular}{cc}
\toprule
Environment & File or Object \\
\midrule
MS Word  & Word document  \\
 & Excel file     \\
iTunes & \\
Typewriter & \\
Jupyter & \\
 & .py \\
\bottomrule
\end{tabular}
\end{center}

\item Run the \verb|maddison_data_input.ipnyb| Python code example.
\begin{itemize}
\item Go to my \verb|data_bootcamp_fall_2018| GitHub repository (link above).
\item Click on week1, get \verb|maddison_data_input.ipnyb|
\begin{itemize}
\item Right click on raw
\item Click \verb|save link as| then your folder window with directory should pop open, save it in your data
\end{itemize}
\item Open file in Jupyter.
\item Run it by clicking on \verb|Cells|, then select \verb|All|
\item What do you see?
\end{itemize}
